Precise Data Flow Analysis\\in the Presence of Correlated Method Calls\footnote{This research was supported by the Natural Sciences and Engineering Research Council of Canada and the Ontario Ministry of Research and Innovation.}

### 2015-06-19 sas2015/main.tex
minor changes
Revert moving eval into its own file
This reverts part of commit f0c85eb906134e1e78bd74221291d1eb96851932.
adding techreport and paper
moving bibliography to prev page
applying Frank's comments
add technical report number as subtitle
move acknowledgement to footnote on first page to save space

\documentclass[runningheads,a4paper]{llncs}

@@

\title{Precise Data Flow Analysis\\in the Presence of Correlated Method Calls}
\titlerunning{Data Flow Analysis in the Presence of Correlated Calls}

\commentout{
\author{
 Marianna Rapoport\inst{1} \and
 Ond\v{r}ej Lhot\'ak\inst{1} \and
 Frank Tip\inst{2}
}
\institute{
 University of Waterloo\\
 \email{ \{mrapoport, olhotak\}@uwaterloo.ca }
  \and
 Samsung Research America\\
 \email{ ftip@samsung.com  }
}
}
\author{\institute{}}

@@

\bibliographystyle{plain}
\bibliography{bib/ref}

\input{content/appendix}
\end{document}

>>>>

@@

\title{Precise Data Flow Analysis\\in the Presence of Correlated Method Calls\footnote{This research was supported by the Natural Sciences and Engineering Research Council of Canada and the Ontario Ministry of Research and Innovation.}}
\titlerunning{Data Flow Analysis in the Presence of Correlated Calls}
\techreport{\subtitle{David R. Cheriton School of Computer Science Technical Report CS-2015-07}}

\author{
 Marianna Rapoport\inst{1} \and
 Ond\v{r}ej Lhot\'ak\inst{1} \and
 Frank Tip\inst{2}
}
\institute{
 University of Waterloo\\
 \email{ \{mrapoport, olhotak\}@uwaterloo.ca }
  \and
 Samsung Research America\\
 \email{ ftip@samsung.com  }
}

%\author{\institute{}}

@@

\vspace{.8cm}
\makeatletter
\patchcmd{\@makeschapterhead}{\vskip40}{\vskip10}{}{}
\makeatother

\bibliographystyle{myplain}
\begingroup
\let\clearpage\relax
\bibliography{bib/ref}
\endgroup

\techreport{\newpage\input{content/appendix.tex}}
\end{document}
